\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2020-12-15 manuscript.Rnw
Fully working code + results

%% For Sweave-based articles about R packages:
%% need no \usepackage{Sweave}
\SweaveOpts{engine = R, eps = FALSE, keep.source = TRUE, eval = TRUE}
<<preliminaries, echo=FALSE, results=hide>>=
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
@

@@

%% -- Models with aggregate level data -----------------------------------------
\section{Economic modeling with aggregate level data} \label{sec:modeling-aggregate}
Health economic models are commonly developed using aggregate level data taken from multiple sources. In these cases it is helpful to be able input model parameters rather than fitting a statistical model. We illustrate with the 4 state disease progression model displayed in Figure~\ref{fig:four-state-model}. Patients advance between successively more severe disease states. It is possible to move from State 2 back to State 1 but recovery is not possible from State 3. Death can occur from any state.

\begin{figure}[h]
\centering
\begin{tikzpicture}
% States
\node[draw, minimum height=1cm, minimum width=2cm, font=\footnotesize] (S1) {\textbf{State 1}};
\node[draw, minimum height=1cm, minimum width=2cm, font=\footnotesize] (S2) [right = of S1] {\textbf{State 2}};
\node[draw, minimum height=1cm, minimum width=2cm, font=\footnotesize] (S3) [right = of S2] {\textbf{State 3}};
\node[draw, minimum height=1cm, minimum width=2cm, font=\footnotesize] (D) [below = of S2] {\textbf{Death}};

% Arrows
\draw [thick, <->] (S1.east) -- (S2.west);
\draw [thick, ->] (S2.east) -- (S3.west);
\draw [thick, ->] (S1.south) -- (D.west);
\draw [thick, ->] (S2.south) -- (D.north);
\draw [thick, ->] (S3.south) -- (D.east);

\end{tikzpicture}
\caption{Four state disease progression model}\label{fig:four-state-model}
\end{figure}

There are 3 treatment strategies: standard of care (SOC) and two new interventions (New 1 and New 2). For illustration, we will consider a target population approximated by two representative patients of age 60 and 70. The 60-year old patient represents $1/3$ of all patients with the disease while the 70-year old patient represents $2/3$. The \code{hesim_data} class is used to store this data.

<<>>=
library("hesim")
library("data.table")
strategies <- data.table(
  strategy_id = 1:3,
  strategy_name = c("SOC", "New 1", "New 2")
)
patients <- data.table(
  patient_id = 1:2,
  grp_id = 1:2,
  age = c(60, 70),
  patient_wt = c(1/3, 2/3)
)
hesim_dat <- hesim_data(
  strategies = strategies,
  patients = patients
)
print(hesim_dat)
@

\subsection{Cohort model}
\subsubsection{Parameterization}
Model parameters related to transition probabilities are obtained from a hypothetical analysis of a natural history cohort. If data is not collected at unevenly spaced intervals, then transitions can be described with transition intensity matrices, $Q$, by fitting a continuous time multi-state model designed for panel data (e.g., with the \proglang{R} package \pkg{msm}) \citep{jackson2011multi}. We assume that regression coefficients and a covariance matrix for $Q$ are available from such an analysis.

<<q_coef, echo = FALSE>>=
trans <- c("1->2", "1->4", "2->1", "2->3", "3->4")
q_coef_int <- log(c(.9, .2, .5, 1.1, 1.5))
q_coef_time <- rep(log(1.2), 5)
q_coef_age <- rep(log(1.05), 5)
q_coef_soc <- data.table(
  trans = rep(trans, 3),
  var = rep(c("intercept", "time[2,Inf)", "age"), each = 5),
  loghr = c(q_coef_int, q_coef_time, q_coef_age)
)
@

<<q_vcov, echo = FALSE>>=
n_vars <- nrow(q_coef_soc)
A <- matrix(runif(n_vars^2) * 2 - 1, ncol = 15)/30
q_vcov_soc <- t(A) %*% A
@

<<q_vcov_print>>=
q_vcov_soc[1:4, 1:4]
@

If many studies are available, then relative treatment effects can be estimated by means of a network meta-analysis. We assume that an NMA was performed to estimate the relative risk of transitions from state 1 to both state 2 and death. Treatment strategy 1 was the reference arm. Estimation is performed in terms of the log relative risk since it is approximately normally distributed.

The utility associated with each state is assumed to follow a beta distribution, which is bounded between 0 and 1. The beta distribution is defined in terms of 2 shape parameters, but can be derived from the mean and standard error using the method of moments. Point estimates for utility in states 1, 2, and 3 are 0.9, 0.75, and 0.5, respectively. Standard errors in the same three states are 0.02, 0.03, and 0.05. Utility is always assumed to be 0 in death states in \pkg{hesim}.

<<params>>=
params <- list(
  q_coef_soc = q_coef_soc,
  q_vcov_soc = q_vcov_soc,
  lrr_est = c(log(.80), log(.71)),
  lrr_se = c(log(.06), log(.08)),
  u_mean = c(.9, .75, .05),
  u_se = c(.02, .03, .05)
)
@

\subsection{Individual model}

%% -- Models with patient level data -------------------------------------------
\section{Economic modeling with patient level data} \label{sec:modeling-patient}

\subsection{Partitioned survival analysis}

\subsection{Multi-state model}

%% -- Cost-effectiveness analysis ----------------------------------------------
\section{Cost-effectiveness analysis} \label{sec:cea}

>>>>

%% For Sweave-based articles about R packages:
%% need no \usepackage{Sweave}

<<include=FALSE>>=
library(knitr)
knitr::render_sweave()
opts_chunk$set(
  engine="R", tidy = FALSE, eval = TRUE, cache = TRUE,
  fig.height = 5, fig.width = 7
)
@

<<preliminaries, echo=FALSE, results="hide">>=
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
ggplot2::theme_set(ggplot2::theme_bw())
set.seed(102)
@

@@

%% -- Illustrative example -----------------------------------------------------
\section{Illustrative example} \label{sec:illustrative-example}

\begin{figure}[h]
\centering
\begin{tikzpicture}
% States
\node[draw, minimum height=1cm, minimum width=2.5cm, font=\footnotesize] (S) {\textbf{Stable}};
\node[draw, minimum height=1cm, minimum width=2.5cm, font=\footnotesize] (P) [right = of S] {\textbf{Progression}};
\node[draw, minimum height=1cm, minimum width=2.5cm, font=\footnotesize] (D) [right = of P] {\textbf{Death}};

% Arrows
\draw [thick, ->] (S.east) -- (P.west);
\draw [thick, ->] (P.east) -- (D.west);
\draw [thick, ->] (S.north) to [bend left = 20] (D.north);

\end{tikzpicture}
\caption{Three state model of disease progression in oncology}\label{fig:three-state-model}
\end{figure}

<<tmat>>=
tmat <- rbind(
  c(NA, 1, 2),
  c(NA, NA, 3),
  c(NA, NA, NA)
)
colnames(tmat) <- rownames(tmat) <- c("Stable", "Progression", "Dead")
print(tmat)
@

<<hesim_data>>=
library("hesim")
library("data.table")
n_patients <- 1000
patients <- data.table(
  patient_id = 1:n_patients,
  age = rnorm(n_patients, mean = 45, sd = 7),
  female = rbinom(n_patients, size = 1, prob = .51)
)

states <- data.table(
  state_id = c(1, 2),
  state_name = c("Stable", "Progression") # Non-death health states
)
n_states <- nrow(states)

strategies <- data.frame(
  strategy_id = 1:3,
  strategy_name = c("SOC", "New 1", "New 2"),
  soc = c(1, 0, 0),
  new1 = c(0, 1, 0),
  new2 = c(0, 0, 1)
)
n_strategies <- nrow(strategies)

hesim_dat <- hesim_data(
  strategies = strategies,
  patients = patients,
  states = states
)
print(hesim_dat)
@

%% -- Individual continuous time state transition model ------------------------
\subsection{Individual continuous time state transition model}

\subsubsection{Parameterization}

<<ictstm_data>>=
onc3[patient_id %in% c(1, 2)]
@

<<ictstm_fits>>=
library("flexsurv")
n_trans <- max(tmat, na.rm = TRUE) 
wei_fits <- vector(length = n_trans, mode = "list")
f <- as.formula(Surv(time, status) ~ factor(strategy_name) + female + age)
for (i in 1:length(wei_fits)){
  if (i == 3) f <- update.formula(f, .~.-factor(strategy_name)) 
  wei_fits[[i]] <- flexsurvreg(f, data = onc3, 
                               subset = (transition_id == i),
                               dist = "weibull")
}
wei_fits <- flexsurvreg_list(wei_fits)
@

<<ictstm_utility>>=
utility_tbl <- stateval_tbl(
  data.table(state_id = states$state_id,
             mean = c(.8, .6),
             se = c(0.02, .05)
  ),
  dist = "beta",
  hesim_data = hesim_dat)
print(utility_tbl)
@

<<ictstm_medcosts>>=
medcost_tbl <- stateval_tbl(
  data.table(state_id = states$state_id,
             mean = c(2000, 9500),
             se = c(2000, 9500)
  ),
  dist = "gamma",
  hesim_data = hesim_dat)
print(medcost_tbl)
@

<<ictstm_drugcost_setup, echo=FALSE, results="hide">>=
n_times <- 2
n_i <- n_states * n_times
drugcost_dt <-  data.table(
    strategy_id = rep(strategies$strategy_id, each = n_i),
    state_id = rep(rep(states$state_id, each = n_times), n_strategies),
    time_start = rep(c(0, 3/12), n_states * n_strategies),
    est = c(rep(2000, n_i -1), 1500, 
            rep(12000, n_i -1), 1000,
            rep(15000, n_i - 1), 1200
            ) 
)
@

<<ictstm_drugcost>>=
drugcost_tbl <- stateval_tbl(
  drugcost_dt,
  dist = "fixed",
  hesim_data = hesim_dat
)
@

\subsubsection{Simulation}
<<ictstm_n_samples>>=
n_samples <- 100
@

<<ictstm_transmod_data>>=
transmod_data <- expand(hesim_dat,
                        by = c("strategies", "patients"))
head(transmod_data)
@

<<ictstm_transmod>>=
transmod <- create_IndivCtstmTrans(wei_fits, transmod_data,
                                   trans_mat = tmat, n = n_samples,
                                   clock = "reset",
                                   start_age = patients$age)
@

<<ictstm_stvalmods>>=
# Utility
utilitymod <- create_StateVals(utility_tbl, n = n_samples)

# Costs
drugcostmod <- create_StateVals(drugcost_tbl, n = n_samples,
                                time_reset = TRUE)
medcostmod <- create_StateVals(medcost_tbl, n = n_samples)
costmods <- list(Drug = drugcostmod,
                 Medical = medcostmod)
@

<<ictstm_econmod>>=
ictstm <- IndivCtstm$new(trans_model = transmod,
                         utility_model = utilitymod,
                         cost_models = costmods)
@

<<ictstm_sim_disease>>=
ictstm$sim_disease(max_age = 100)
head(ictstm$disprog_)
@

<<ictstm_sim_stateprobs>>=
ictstm$sim_stateprobs(t = seq(0, 30 , 1/12))
head(ictstm$stateprobs_)
@

<<ictstm_summarize_stateprobs, echo=FALSE, results="hide">>=
add_state_name <- function(x){
  x[, state_name := factor(state_id,
                           levels = 1:nrow(tmat),
                           labels = colnames(tmat))]
}

add_strategy_name <- function(x) {
  x[, strategy_name := factor(strategy_id, 
                              labels = c("SOC", "New 1", "New 2"))]
}

summarize_stprobs <- function(stateprobs){
  x <- stateprobs[, .(prob_mean = mean(prob)),
                  by = c("strategy_id", "state_id", "t")]
  add_state_name(x)
  add_strategy_name(x)
  return(x[, ])
}
@

<<ictstm_plot_stateprobs, echo = FALSE, include = FALSE>>=
library("ggplot2")
stprobs <- summarize_stprobs(ictstm$stateprobs_)
ggplot(stprobs, 
       aes(x = t, y = prob_mean, col = strategy_name)) +
  geom_line() + facet_wrap(~state_name) +
  xlab("Years") + ylab("Probability in health state") +
  scale_color_discrete(name = "Strategy") +
  theme(legend.position = "bottom") 
@

\begin{figure}[t!]
\centering
\includegraphics{figure/ictstm_plot_stateprobs-1.pdf}
\caption{Mean simulated state probabilities from the probabilistic sensitivity analysis} \label{fig:ictstm-stprobs}
\end{figure}

<<ictstm_sim_qalys>>=
ictstm$sim_qalys(dr = c(0,.03))
head(ictstm$qalys_)
@

<<ictstm_sim_costs>>=
ictstm$sim_costs(dr = .03)
head(ictstm$costs_)
@

<<ictstm_icer>>=
ce_sim_ictstm <- ictstm$summarize()
cea_pw_ictstm <- cea_pw(ce_sim_ictstm, comparator = 1,
                        dr_qalys = .03, dr_costs = .03,
                        k = seq(0, 25000, 500))
icer_tbl(cea_pw_ictstm, colnames = strategies$strategy_name,
         k = 100000)
@

%% -- Partitioned survival model -----------------------------------------------
\subsection{Partitioned survival model}
<<psm_hesim_data>>=
hesim_dat$patients <- data.table(
  patient_id = 1:4,
  patient_wt = rep(1/4, 4),
  age = c(55, 65, 55, 65),
  female = c(1, 1, 0, 0)
)
@

\subsubsection{Parameterization}
<<psm_data>>=
surv_est_data <- as_pfs_os(onc3, patient_vars = c("patient_id", "female", "age", 
                                                  "strategy_name"))
surv_est_data[patient_id %in% c(1, 2)]
@

<<psm_fits>>=
fit_pfs_wei <- flexsurv::flexsurvreg(
  Surv(pfs_time, pfs_status) ~ strategy_name + female,
  data = surv_est_data,
  dist = "weibull")

fit_os_wei <- flexsurvreg(
  Surv(os_time, os_status) ~ strategy_name + female,
  data = surv_est_data,
  dist = "weibull")

psmfit_wei <- flexsurvreg_list(fit_pfs_wei, fit_os_wei)
@

<<psm_stateval_tbl>>=
attr(utility_tbl, "patients") <- hesim_dat$patients
attr(medcost_tbl, "patients") <- hesim_dat$patients
@

<<psm_drugcost>>=
drugcost_tbl <- stateval_tbl(
  data.table(strategy_id = strategies$strategy_id,
             est = c(2000, 12000, 15000)),
  dist = "fixed",
  hesim_data = hesim_dat)
print(drugcost_tbl)
@

\subsubsection{Simulation}

<<psm_survmods_data>>=
survmods_data <- expand(hesim_dat, by = c("strategies", "patients"))
head(survmods_data)
@

<<psm_survmods>>=
survmods <- create_PsmCurves(psmfit_wei,
                             input_data = survmods_data,
                             n = n_samples,
                             bootstrap = FALSE, est_data = surv_est_data)
@

<<psm_stvalmods>>=
utilitymod <- create_StateVals(utility_tbl, n = n_samples)
drugcostmod <- create_StateVals(drugcost_tbl, n = n_samples)
medcostmod <- create_StateVals(medcost_tbl, n = n_samples)
costmods <- list(Drug = drugcostmod, Medical = medcostmod)
@

<<psm_econmod>>=
psm <- Psm$new(survival_models = survmods,
               utility_model = utilitymod,
               cost_models = costmods)
@

<<psm_sim_survival>>=
times <- seq(0, 20, by = .1)
psm$sim_survival(t = times)
head(psm$survival_)
@

<<psm_plot_survival, echo = FALSE, include = FALSE>>=
# Survival curve plotting data
surv_means <- psm$survival_[, lapply(.SD, weighted.mean, w = patient_wt),
                                by = c("strategy_id", "curve", "t"),
                               .SDcols = "survival"]
surv_mean_min <- surv_means[curve != 2][, curve := curve + 1]
setnames(surv_mean_min, "survival", "survival_min")
surv_means <- merge(surv_means, surv_mean_min,
                    by = c("strategy_id", "curve", "t"),
                    all.x = TRUE)
surv_means[, survival_min := ifelse(curve == 1, 0, survival_min)]
surv_means[, curve := factor(curve, labels = c("PFS", "OS"))]
surv_means[, strategy_name := factor(strategy_id, labels = c("SOC", "New 1", "New 2"))]

# Plot
ggplot(surv_means, aes(x = t, y = survival, fill = curve)) +
  geom_line(aes(col = curve)) +
  facet_wrap(~strategy_name) +
  geom_ribbon(aes(ymin = survival_min, ymax = survival), alpha = .5) +
  xlab("Years") + ylab("Proportion surviving") +
  scale_color_discrete(name = "Survival curve") +
  guides(fill = FALSE) +
  theme_bw() +
  theme(legend.position = "bottom") 
@

\begin{figure}[t!]
\centering
\includegraphics{figure/psm_plot_survival-1.pdf}
\caption{Mean progression free survival and overall survival, weighted by weight of each patient in the target population. Solid and dotted lines represent means and 95\% confidence intervals from the probabilistic sensitivity analysis, respectively. 
weighted} \label{fig:psm-survival}
\end{figure}

<<psm_sim_stateprobs>>=
psm$sim_stateprobs()
psm$stateprobs_[sample == 1 & patient_id == 1 & state_id == 2 & t == 12]
@

<<psm_costs_qalys>>=
psm$sim_costs(dr = .03)
psm$sim_qalys(dr = .03)
@

<<psm_icer>>=
ce_sim_psm <- psm$summarize()
cea_pw_psm <- cea_pw(ce_sim_psm, comparator = 1,
                     dr_qalys = .03, dr_costs = .03,
                     k = seq(0, 25000, 500))
icer_tbl(cea_pw_psm, colnames = strategies$strategy_name,
         k = 100000)
@

\subsection{Cohort disctete time state transition model}

\subsubsection{Parameterization}

<<cdtstm_fit_soc, warning = FALSE>>=
library("msm")
qinit <- matrix(0, nrow = 3, ncol = 3)
qinit[1, 2] <-  0.28
qinit[1, 3] <-  0.013
qinit[2, 3] <-  0.10
msm_fit <- msm(state_id ~ time, subject = patient_id, 
               data = onc3p[strategy_name == "SOC"],
               exacttimes = FALSE,
               covariates = ~ age + female,
               qmatrix = qinit, gen.inits = FALSE)
@

<<msm_exact, eval = FALSE>>=
# msm with exact transition times
tmat2 <- tmat; tmat2[is.na(tmat2)] <- 0
msm_efit <- msm(state_id ~ time, subject = patient_id, 
                data = onc3p[strategy_name == "SOC"],
                qmatrix = tmat2, exacttimes = TRUE)

# flexsurv with exponential model
library("flexsurv")
exp_fits <- vector(length = n_trans, mode = "list")
for (i in 1:length(wei_fits)){
  exp_fits[[i]] <- flexsurvreg(Surv(time, status) ~ 1, data = onc3, 
                               subset = (transition_id == i & 
                                         strategy_name == "SOC"),
                               dist = "exponential")
}

# Compare
msm_efit
exp_fits[[1]]$res
exp_fits[[2]]$res
exp_fits[[3]]$res
@

<<cdtstm_params>>=
params2 <- list(
  lrr_12_est = c(soc = log(1), new1 = log(.80), new2 = log(.71)),
  lrr_12_se = c(soc = 0, new1 = .03, new2 = .04),
  lrr_13_est = c(soc = log(1), new1 = log(.90), new2 = log(.85)),
  lrr_13_se = c(soc = 0, new1 = .02, new2 = .03),
  u_mean = c(s1 = .9, s2 = .75, s3 = .05),
  u_se = c(s1 = .02, s2 = .03, s3 = .05)
)

params2_def <- define_rng({
  list(
    rr_12 = lognormal_rng(lrr_12_est, lrr_12_se),
    rr_13 = lognormal_rng(lrr_13_est, lrr_13_se),
    u = beta_rng(mean = u_mean, sd = u_se)
  )}, n = n_samples)

params2_rng <- eval_rng(params2_def, params2)
@

<<qmat_soc>>=
transmod_data <- survmods_data
qmat_soc <- qmatrix(msm_fit, newdata = transmod_data[strategy_name == "SOC"],
                    uncertainty = "normal", n = n_samples)
qmat_soc[,, 1]
@

<<pmat_soc>>=
cycle_len <- 1/4
pmat_soc <- expmat(qmat_soc, t = cycle_len)
pmat_soc[,, 1]
@

<<transprobs_id>>=
tpmat_id <- tpmatrix_id(transmod_data, n_samples)
head(tpmat_id)
@

<<xbeta>>=
xbeta <- function(x, beta) c(x %*% t(beta))
@

<<rr>>=
x_rr <- as.matrix(transmod_data[, .(soc, new1, new2)])
rr <- cbind(xbeta(x_rr, params2_rng$rr_12),
            xbeta(x_rr, params2_rng$rr_13))
@

<<apply_rr>>=
pmat <- apply_rr(pmat_soc, rr = rr,
                 index = list(c(1, 2), c(1, 3)))
@

<<tparams_transprobs>>=
tprobs <- tparams_transprobs(pmat, tpmat_id)
@

\subsubsection{Simulation}
<<dtstm_transmod>>=
transmod <- CohortDtstmTrans$new(params = tprobs, cycle_length = cycle_len)
@

<<dtstm_econmod>>=
cdtstm <- CohortDtstm$new(trans_model = transmod,
                         utility_model = psm$utility_model,
                         cost_models = psm$cost_models)
@

<<cdtstm_sim_stateprobs>>=
cdtstm$sim_stateprobs(n_cycles = 30/cycle_len)
@

<<cdtstm_plot_stateprobs, echo = FALSE, include = FALSE>>=
stprobs_tot <- cdtstm$stateprobs_[, lapply(.SD, weighted.mean, w = patient_wt),
                                   by = c("sample", "strategy_id", "state_id", "t"),
                                   .SDcols = "prob"]
stprobs_summary <- summarize_stprobs(stprobs_tot)
ggplot(stprobs_summary, aes(x = t, y = prob_mean)) +
  geom_line(aes(col = strategy_name)) +
  # geom_ribbon(aes(x = t, ymin = prob_lower, ymax = prob_upper,
  #                 fill = strategy_name), alpha = .3) +
  facet_wrap(~state_name) +
  xlab("Year") + ylab("Probability") +
  scale_fill_discrete("Strategy") + scale_color_discrete("Strategy")
@

<<cdtstm_sim_qalys_costs>>=
cdtstm$sim_qalys(dr = .03)
cdtstm$sim_costs(dr = .03)
@

<<cdtstm_icer>>=
ce_sim_cdtstm <- cdtstm$summarize()
cea_pw_cdtstm <- cea_pw(ce_sim_cdtstm, comparator = 1, 
                        dr_costs = .03, dr_qalys = .03)
icer_tbl(cea_pw_cdtstm, output = "data.table")
@

%% -- Cost-effectiveness analysis ----------------------------------------------
\section{Cost-effectiveness analysis} \label{sec:cea}
<<cea>>=
wtp <- seq(0, 250000, 500) # Willingness to pay per QALY
cea_ictstm <- cea(ce_sim_ictstm, dr_costs = .03, dr_qalys = .03, k = wtp)
@

<<ce_plane>>=
library("scales")
strategy_factor <- function (x) {
  factor(x, levels = 1:3, labels = c("SOC", "New 1", "New 2"))
}

xlim <- ceiling(max(cea_pw_ictstm$delta[, ie]) * 1.2)
ylim <- max(cea_pw_ictstm$delta[, ic]) * 1.2
ggplot(cea_pw_ictstm$delta,
       aes(x = ie, y = ic, col = strategy_factor(strategy_id))) +
  geom_jitter(size = .5)  +
  xlab("Incremental QALYs") +
  ylab("Incremental cost") +
  scale_y_continuous(limits = c(-ylim, ylim),
                     labels = scales::dollar) +
  scale_x_continuous(limits = c(-xlim, xlim), breaks = seq(-2, 2, .5)) +
  theme(legend.position = "bottom") +
  scale_colour_discrete(name = "Strategy") +
  geom_abline(slope = 100000, linetype = "dashed") +
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = 0)
@

<<ceac>>=
ggplot(cea_ictstm$mce,
       aes(x = k, y = prob, col = strategy_factor(strategy_id))) +
  geom_line() +
  xlab("Willingness to pay") +
  ylab("Probability most cost-effective") +
  scale_x_continuous(breaks = seq(0, max(wtp), length.out = 6),
                     label = scales::dollar) +
  theme(legend.position = "bottom")
@

<<evpi>>=
ggplot(cea_ictstm$evpi, aes(x = k, y = evpi)) +
  geom_line()  +
  xlab("Willingness to pay") +
  ylab("Expected value of perfect information") +
  scale_x_continuous(breaks = seq(0, max(wtp), length.out = 6),
                     label = scales::dollar) +
  scale_y_continuous(label = scales::dollar) +
  theme(legend.position = "bottom")
@
